Adversarial Training against Systematic Uncertainty

### 2016-09-06 tex/paper.tex
save

\begin{proposition}
    \glnote{It remains to prove that the procedure of Algorithm 1
    converges towards that saddle point. The proof should be similar to the proof of convergence in the GAN paper.}
\end{proposition}

\glnote{We should further discuss that in practice, the equality in Prop 2 may never hold.
We should discuss in which circumstances. In such case, the pivotal quantity
constraint can however be enforced by outweighting the ${\cal L}_r$ term, resulting in a
trade-off between classifier optimality and pivotality.}

>>>>

Proposition~\ref{prop:2} suggests that if at each step of
Algorithm~\ref{alg:adversarial-training} the adversary $r$ is allowed to reach
its optimum given $f$ (e.g., by setting $K$ sufficiently high) and if $f$ is
updated to improve ${\cal L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$, then $f$
should converge to a classifier which is both optimal and pivotal, provided such
a classifier exists. On many problems of interest though, such a classifier may
not exist, in which case the lower bound $H(p_{Y|X}) - H(p_Z) < {\cal
L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$ is strict: $f$ can either be an optimal
classifier or a pivotal quantity, but not both simultaneously. Accordingly the value
function $E$ can be rewritten as
\begin{equation}
    E_\lambda(\theta_f, \theta_r) = {\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r),
\end{equation}
where $\lambda \geq 0$ is a hyper-parameter controlling the trade-off between the performance of $f$
and its independence with respect to the nuisance parameter. Setting $\lambda$ to a large
value will preferrably enforces $f$ to be pivotal while setting $\lambda$ to a value close to $0$
will rather constraint $f$ to be optimal.
